Wi-Fi Based Handwritten Signature Verification Using a Triplet Network

### 2019-10-08 191001_Paper_BDML_v2/bdml_v2_R1.tex
paper_conf: v2_r1

\maketitle
\begin{abstract}
       In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
       To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
       Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
       Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
\end{abstract}

@@

%Intro
\section{Introduction}
Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}. Among these behavioral biometrics, the signature-based user authentication~\cite{fahmy2010online,sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic}.
With the help of sensors such as the depth camera~\cite{jeon2012system,malik20183dairsig} or a mobile sensor~\cite{ketabdar2012magnetic}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic,sesa2012information}.

@@

The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
\end{itemize}

@@

% related works
\section{Related works}
\subsection{Triplet network}
% triplet network
The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features. The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or under different occasions are to be associated. In order to address our challenging Wi-Fi based verification task, we adopt a triplet network which optimizes the input data space so that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.

The triplet network receives triplet pairs of data as its input. These data triplets are constructed based on a combination of the input data. Since not all triplet samples contribute to the desired classification, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training. In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplets from a small number of classes (persons) in each iteration. Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence. They utilized a large mini-batch at each training iteration and selected the triplets based on network training instead of random sampling. However, this strategy needed a few thousands of exemplar mini-batches in every training iteration for triplet pairs selection. This results in a heavy computational load in training. In order to make use of the small sample training size as well as to speed up the triplet training process, we adopt the kernel and range space method for the learning.

@@

% Karnet structure and mining samples.
Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network output.
Then the multilayer neural network can be written in equation form as follows:
\begin{equation}
    \mathbf{G}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

@@

The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network. For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set. The positive and negative samples (respectively $x_{pos,i}$ and $x_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
The triplet loss function is formulated based on a summation of the difference between the positive distance (the $L2$ distance between the anchor vector and the positive vector) and the negative distance (the $L2$ distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]},0 \right),\label{triplet}
\end{equation}
where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the $L2$ distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\subsubsection{Performance evaluation:}
The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve. For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded. For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA)~\cite{turk1991eigenfaces} with LSE, the support vector machine (SVM)~\cite{vapnik2013nature} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
\begin{table}
\centering
    \caption{The network structure of KAR space learning.}
    \label{tab2}
    \begin{tabular}{|c|c|c|} \hline
     Layer   & Size     & Activation \\ \hline
     Input   & 500$\times$30$\times$6 &            \\ \hline
     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\ \hline
     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\ \hline
     Output  & 1$\times$1$\times$50   &            \\\hline
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with $L2$ penalty of 0.0002 except for the output layer. The output layer was regularized using an $L2$ penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE, SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
\begin{table}
\centering
    \caption{The structure of ConvNet model. For the convolution layer, the kernel is specified as (m$\times$m) sized filter $\times$ (\# of filters) / (\# of stride). For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.}
    \label{tab1}
    \begin{tabular}{|c|c|c|c|} \hline
     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\ \hline
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\ \hline
     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\ \hline
     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\ \hline
     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\ \hline
     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\ \hline
     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\ \hline
     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\ \hline
     Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting. For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER. However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods. This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods. The test EER performance of the proposed system is 19.35\%. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER. The Siamese network is also a metric learning system, but differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
\begin{table*}
\centering
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
    \label{tab3}
    \begin{tabular}{|c|c|c|l|} \hline
    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
    LSE                                    & 35.40 & 48.44           &                           \\  \hline
    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\  \hline
    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\  \hline
    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\  \hline
    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\ \hline
    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\  \hline
    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\  \hline
    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\ \hline
    \end{tabular}
\end{table*}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This research was supported by Basic Science Research
Program through the National Research Foundation of Korea
(NRF) funded by the Ministry of Education, Science and
Technology.

\noindent(NRF-2018R1D1A1A09081956)

>>>>

\maketitle
\begin{abstract}
Attributed to the omnipresence of the radio signals for communications, sensing and recognition utilizing the Wi-Fi signals has significant advantage  in terms of accessibility over conventional sensing means such as the camera. However, utilizing the raw Wi-Fi signals to capture in-air handwritten signatures for identity verification is yet a challenging task.
In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
A triplet network is adopted to learn the correlation between the captured signals and the user identities.
To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
Subsequently, the triplet network is trained on a ConvNet structure based on the mined triplet inputs. 
Our experiments on a Wi-Fi dataset collected in-house show encouraging verification accuracy with faster training loss convergence comparing with that of the baseline triplet network and the Siamese network.
\end{abstract}

@@

%Intro
\section{Introduction}
Over recent years, several behavioral biometric traits have attracted attention in view of their rigid physical body independence. Among these behavioral biometrics, the signature-based user authentication~\cite{fahmy2010online,sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic,moon2017air}.
With the help of sensors such as the depth camera~\cite{jeon2012system,malik20183dairsig} or a mobile sensor~\cite{ketabdar2012magnetic}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems~\cite{zhu2000biometric,jain2002line,sesa2012information}.

@@

The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
\item Provision of an experimental study using Wi-Fi handwritten signature dataset which was collected in-house based on 50 subjects.
\end{itemize}

@@

% related works
\section{Related works}
\subsection{Triplet network}
% triplet network
The triplet network is considered a metric learning based model which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,wang2016joint} where the individual identities are matched based on discriminative image features. The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or under different occasions are to be associated. In order to address our challenging Wi-Fi based verification task, we adopt a triplet network which optimizes the input data space so that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.

The triplet network receives triplet pairs of data as its input. These data triplets are constructed based on a combination of the input data. Since not all triplet samples contribute to the desired classification, recent attention has been paid to the choice of relevant input pairs for training. In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplets from a small number of classes (persons) in each iteration. In~\cite{schroff2015facenet}, a triplet mining process was implemented to speed up the training convergence. They utilized a large mini-batch at each training iteration and selected the triplets based on network training instead of random sampling. However, this strategy needed a few thousands of exemplar mini-batches in every training iteration for triplet pairs selection. This results in a heavy computational load in training. In order to make use of the small sample training size as well as to speed up the triplet training process, we adopt the kernel and the range space method for the learning.

@@

% Karnet structure and mining samples.
Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network output.
Then the multilayer neural network can be written in equation form as follows:
\begin{equation}
    \mathbf{G}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\\\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

@@

The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network. For the $i^{th}$ network input $\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \\ \mathbf{x}_{neg,i}\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set. The positive and negative samples (respectively $x_{pos,i}$ and $x_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
The triplet loss function is formulated based on a summation of the difference between the positive distance (the $L2$ distance between the anchor vector and the positive vector) and the negative distance (the $L2$ distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]},0 \right),\label{triplet}
\end{equation}
where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the $L2$ distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\subsubsection{Performance evaluation:}
The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve. For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded. For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA)~\cite{turk1991eigenfaces} with LSE, the support vector machine (SVM)~\cite{boser1992training} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
\begin{table}
\centering
    \caption{The network structure of KAR space learning.}
    \label{tab2}
    \begin{tabular}{|l|l|l|} \hline
     Layer   & Size     & Activation \\ \hline
     Input   & 500$\times$30$\times$6 &            \\ \hline
     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\ \hline
     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\ \hline
     Output  & 1$\times$1$\times$50   &            \\\hline
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with $L2$ penalty of 0.0002 except for the output layer. The output layer was regularized using an $L2$ penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE, SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
\begin{table}
\centering
    \caption{The structure of ConvNet model. For the convolution layer, the kernel is specified as (m$\times$m) sized filter $\times$ (\# of filters) / (\# of stride). For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.}
    \label{tab1}
    \begin{tabular}{|l|l|l|l|} \hline
     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\ \hline
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\ \hline
     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\ \hline
     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\ \hline
     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\ \hline
     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\ \hline
     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\ \hline
     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\ \hline
     Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting. For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER. However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods. This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods. The test EER performance of the proposed system is 19.35\%. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER. The Siamese network is also a metric learning system, but differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
\begin{table*}
\centering
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
    \label{tab3}
    \begin{tabular}{|l|c|c|l|} \hline
    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
    LSE                                    & 35.40 & 48.44           &                           \\  \hline
    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\  \hline
    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\  \hline
    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\  \hline
    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\ \hline
    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\  \hline
    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\  \hline
    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\ \hline
    \end{tabular}
\end{table*}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This research was supported by Basic Science Research
Program through the National Research Foundation of Korea
(NRF) funded by the Ministry of Education, Science and
Technology (NRF-2018R1D1A1A09081956).

%\noindent(NRF-2018R1D1A1A09081956)
